---
title: "2-analysis"
author: "bernard-liew"
date: "2021-02-19"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# Load package

```{r message=FALSE, warning=FALSE}
# Helper
library (tidyverse)
library (arsenal)
library (cowplot)

# Modelling
library (huge)
library (bootnet)
library (qgraph)
library (NetworkComparisonTest)
library (EGAnet)

# Parallel
library (furrr)

# Styling
library (kableExtra)
library (officer)
library (flextable)

```

# Import 

Binarize `rts_6` and `rts_12`.

`rts_6` = `"no"` if either missing `NA`, `"na_no_prior"` or `"no"`. Everything else is `"yes"`.

`rts_12` = `"no"` if either missing `"no"`, or `"yes_lower"`. Everything else is `"yes"`.
```{r}
df <- readRDS ("output/dat_acl.RDS") %>%
  mutate (rts_6binary = ifelse (rts_6 %in% c("na_no_prior", "no"), "no", 
                                ifelse (rts_6 %in% c("NA"), "na", "yes")),
          rts_12binary = ifelse (rts_12 %in% c("no", "yes_lower"), "no", "yes"))


```

```{r, include = FALSE}
res <- readRDS ("output/nw_res.RDS")

sf <- paste0("q", c(1,2,3,5,6,7)) 
node_col <- ifelse (names (res$data[[1]]) %in% sf, "lightblue", "white")
```


# Descriptive statistics 

```{r}
df_plot <- res %>%
  select (id,data) %>%
  unnest (data) %>%
  pivot_longer(cols = starts_with("q"),
               names_to = "Items",
               values_to = "val") %>%
  mutate (Items = factor (Items, levels = names (res$data[[1]])))

df_plot <- df_plot %>%
  group_by(id, Items) %>%
  summarise(Mean = mean (val, na.rm = TRUE),
            Sd = sd (val, na.rm = TRUE)) %>%
  mutate (id = factor (id, levels = c("6mo","12mo","6moNo","6moYes","12moNo", "12moYes")))

 f <- ggplot (df_plot) +
  geom_point(aes (x = Items, y = Mean),  
             stat = "identity") +
  geom_errorbar(aes (x = Items, 
                     ymin = Mean - Sd, 
                     ymax = Mean + Sd), 
                width = 0) +
  facet_wrap(~ id, scales = "fixed", ncol = 2) +
  labs (x = "Items",
        y = "Score") +
  theme_cowplot() 

pdf(width = 15, height = 8, file = "manuscript/sm_fig1.pdf")
f
dev.off()
```

# Network analysis

## Create datasets

```{r message=FALSE, warning=FALSE, eval = FALSE}
# 6th month RSI data
dat1 <- df%>%
    select (matches ("_6")) %>%
    select (!matches ("ax_6m|ax_12m|aclrsi|rts_"))
# 12th month RSI data
dat2 <- df%>%
    select (matches ("_12")) %>%
    select (!matches ("ax_6m|ax_12m|aclrsi|rts_"))
# 6th month RSI data on subgroup RTS at 6mo = no
dat3 <- df%>%
    filter (rts_6binary != "na") %>%
    filter (rts_6binary == "no") %>%
    select (matches ("_6")) %>%
    select (!matches ("ax_6m|ax_12m|aclrsi|rts_"))
# 6th month RSI data on subgroup RTS at 6mo = yes
dat4 <- df %>%
    filter (rts_6binary != "na") %>%
    filter (rts_6binary == "yes") %>%
    select (matches ("_6")) %>%
    select (!matches ("ax_6m|ax_12m|aclrsi|rts_"))
# 12th month RSI data on subgroup RTS at 12mo = no
dat5 <- df%>%
    filter (rts_12binary == "no") %>%
    select (matches ("_12")) %>%
    select (!matches ("ax_6m|ax_12m|aclrsi|rts_"))
# 12th month RSI data on subgroup RTS at 12mo = yes
dat6 <- df%>%
    filter (rts_12binary == "yes") %>%
    select (matches ("_12")) %>%
    select (!matches ("ax_6m|ax_12m|aclrsi|rts_"))

var_names <- str_remove (names (dat1), "_6")
names(dat1) <- names(dat2) <- names(dat3) <- names(dat4) <- names(dat5) <- names(dat6) <- paste0("q", 1:ncol (dat1))

res <- tibble (subgrp = c(1:6),
               id = c("6mo", "12mo", "6moNo", "6moYes", "12moNo", "12moYes"),
               data =  list (dat1, dat2, dat3, dat4, dat5, dat6))

```

## Perform analysis

```{r, eval = FALSE}
B <- 1000
plan (multisession)
stats_type <- c("strength", "betweenness", "closeness")

res <- res %>%
  mutate (dat_norm = map (data, huge.npn)) %>%
  mutate (nw = map (dat_norm, estimateNetwork,
                         default="EBICglasso",
                         corMethod = "cor",
                          tuning = 0.5,
                          lambda.min.ratio = 0.001,
                          corArgs =
                            list(method = "pearson",
                                 use = "pairwise.complete.obs"))) %>%
  # Get centrality measures
  mutate (centr = map (nw, centralityTable)) %>%
  mutate (centr_stb = future_map (nw, 
                                  bootnet, 
                                  nBoots = B,
                                  type = "case",
                                  statistics = stats_type,
                                  .options = furrr_options(seed = TRUE))) %>%
  mutate (cor_stb = map (centr_stb,
                         corStability)) %>%
  mutate (edgewts = future_map (nw, 
                                bootnet, 
                                nBoots = B,
                                .options = furrr_options(seed = TRUE)))
   
saveRDS(res,
        "output/nw_res.RDS")  
```



## Results

### Plot network

**Blue edges** - positive correlation. **Red edges **- negative correlation.

The thickness of the edges indicate the magnitude of correlation.

```{r message=FALSE, warning=FALSE, fig.height=9, fig.width=9}

node_font_size <- 1.5
circle_size <- 12
title_font_size <- 3
legend_font_size <- 2

par(mfrow= c(3,2))
# Visualize network
p1 <- plot (res$nw[[1]], title = res$id[[1]], label.cex = node_font_size, vsize = circle_size,
            curve = 0.4, curveAll = TRUE, groups = as.factor (res$ega[[1]]$wc), title.cex = title_font_size)
plot (res$nw[[2]], title = res$id[[2]], layout = p1$layout, label.cex = node_font_size, vsize = circle_size, 
      curve = 0.4, curveAll = TRUE, groups = as.factor (res$ega[[2]]$wc), title.cex = title_font_size)
plot (res$nw[[3]], title = res$id[[3]], layout = p1$layout, label.cex = node_font_size, vsize = circle_size,
      curve = 0.4, curveAll = TRUE, groups = as.factor (res$ega[[3]]$wc), title.cex = title_font_size)
plot (res$nw[[4]], title = res$id[[4]], layout = p1$layout, label.cex = node_font_size, vsize = circle_size,
      curve = 0.4, curveAll = TRUE, groups = as.factor (res$ega[[4]]$wc), title.cex = title_font_size)
plot (res$nw[[5]], title = res$id[[5]], layout = p1$layout, label.cex = node_font_size, vsize = circle_size,
      curve = 0.4, curveAll = TRUE, groups = as.factor (res$ega[[5]]$wc), title.cex = title_font_size)
plot (res$nw[[6]], title = res$id[[6]], layout = p1$layout, label.cex = node_font_size, vsize = circle_size,
      curve = 0.4, curveAll = TRUE, groups = as.factor (res$ega[[6]]$wc), title.cex = title_font_size)
```

```{r, eval = FALSE}
# Export
pdf(width = 25, height = 15, file = "manuscript/fig1.pdf")
par(mfrow= c(3,2))
# Visualize network
par(mfrow= c(3,2))
# Visualize network
p1 <- plot (res$nw[[1]], title = res$id[[1]], label.cex = node_font_size, vsize = circle_size,
            curve = 0.4, curveAll = TRUE, groups = as.factor (res$ega[[1]]$wc), title.cex = title_font_size, legend.cex = legend_font_size)
plot (res$nw[[2]], title = res$id[[2]], layout = p1$layout, label.cex = node_font_size, vsize = circle_size, 
      curve = 0.4, curveAll = TRUE, groups = as.factor (res$ega[[2]]$wc), title.cex = title_font_size, legend.cex = legend_font_size)
plot (res$nw[[3]], title = res$id[[3]], layout = p1$layout, label.cex = node_font_size, vsize = circle_size,
      curve = 0.4, curveAll = TRUE, groups = as.factor (res$ega[[3]]$wc), title.cex = title_font_size, legend.cex = legend_font_size)
plot (res$nw[[4]], title = res$id[[4]], layout = p1$layout, label.cex = node_font_size, vsize = circle_size,
      curve = 0.4, curveAll = TRUE, groups = as.factor (res$ega[[4]]$wc), title.cex = title_font_size, legend.cex = legend_font_size)
plot (res$nw[[5]], title = res$id[[5]], layout = p1$layout, label.cex = node_font_size, vsize = circle_size,
      curve = 0.4, curveAll = TRUE, groups = as.factor (res$ega[[5]]$wc), title.cex = title_font_size, legend.cex = legend_font_size)
plot (res$nw[[6]], title = res$id[[6]], layout = p1$layout, label.cex = node_font_size, vsize = circle_size,
      curve = 0.4, curveAll = TRUE, groups = as.factor (res$ega[[6]]$wc), title.cex = title_font_size, legend.cex = legend_font_size)
dev.off()

```



```{r, include = FALSE, eval = FALSE}
# Easy reporting in manuscript

m = 1

for (n in 1:6) {
  
x <- summary (res$edgewts[[n]]) %>%
  ungroup () %>%
  filter (type == "edge" & sample != 0) %>%
  dplyr::select (id, node1, node2, sample, q2.5, q97.5) %>%
  mutate (samp_abs = abs (sample)) %>%
  slice_max (samp_abs, n = 2) %>%
  mutate_if (is.numeric, round, 2) 



cat ("The edge with the greatest weight magnitude was between", x[[m,"node1"]],
     "and",   x[[m,"node2"]],
     "with a value of", x[[m,"sample"]],
     "([95%CI (", x[[m, "q2.5"]], "to", x[[m,"q97.5"]], "])", "\n")

}
```

### Plot edge weights stability

95% CI of different edge weights that do not overlap are significantly different

```{r message=FALSE, warning=FALSE, fig.height=25, fig.width=9}

w_fig <- map (res$edgewts, plot, order = "sample", CIstyle = "SE")

w_fig <- map (w_fig, ~.x + 
                  theme(text = element_text(size = 16)), 
              include = "all", print = FALSE, scale = "relative")

cowplot::plot_grid(plotlist = w_fig, labels = res$id, vjust = 1, hjust = -1, ncol = 2, nrow = 3)


```

```{r, eval = FALSE, include = FALSE}

# export
w_fig <- map (res$edgewts, plot, order = "sample", CIstyle = "quantiles")

w_fig <- map (w_fig, ~.x + 
                  theme(text = element_text(size = 12)), 
              include = "all", print = FALSE, scale = "relative")

pdf(width = 10, height = 25, file = "manuscript/fig2.pdf")
cowplot::plot_grid(plotlist = w_fig, 
                  labels = res$id, 
                  vjust = 1, hjust = -1, ncol = 2)
dev.off()

```

### Plot centrality

**High centrality** nodes have strong connections to many other nodes, and act as hubs that connect otherwise disparate nodes to one another. **Low centrality** nodes exist on the periphery of the network, with fewer and weaker connections to other nodes of the network.

**Strength** is the sum of the absolute value of its connections with other nodes in the network.

**Closeness** centrality is defined as the inverse of the sum of the distances of the focal node from all the other nodes in the network. Closeness is the average shortest path between a given node and the remaining nodes in the network. Nodes with higher closeness are more proximally connected to the rest of the network.

**Betweenness** is the number of times in which a given node lies on the shortest path between two other nodes.

The greater the value of centrality indices to one, the more important the variable.

```{r message=FALSE, warning=FALSE, fig.height=15, fig.width=9}

c_fig <- map (res$nw, centralityPlot, include = c("Closeness", "Strength", "Betweenness"),  
              print = FALSE, scale = "relative") %>%
  map (~.x + 
                  scale_x_continuous(breaks= c(0, 0.5, 1), lim = c(0, 1)) + 
                  theme(text = element_text(size = 20), 
                        axis.text.x = element_text(angle = 45, hjust = 1)), 
              include = "all", print = FALSE, scale = "relative")

#tiff(width = 15, height = 15, units = "in", res = 100, file = "output/odi_strength.tiff")
cowplot::plot_grid(plotlist = c_fig,  labels = res$id, vjust = 1, hjust = 0, ncol = 2, nrow = 3)
#dev.off()
```

```{r eval = FALSE, include = FALSE}

# export
c_fig <- map (res$nw, centralityPlot, include = c("Closeness", "Strength", "Betweenness"), 
              print = FALSE, scale = "relative") %>%
  map (~.x + 
                  scale_x_continuous(breaks= c(0, 0.5, 1), lim = c(0, 1)) + 
                  theme(text = element_text(size = 20), 
                        axis.text.x = element_text(angle = 45, hjust = 1)), 
              include = "all", print = FALSE, scale = "relative")

pdf(width = 20, height = 15, file = "manuscript/fig3.pdf")
cowplot::plot_grid(plotlist = c_fig, 
                  labels = res$id,
                    vjust = 1, hjust = 0, ncol = 2)
dev.off()

```

```{r, eval = FALSE, include = FALSE}

for (n in seq_along (res$id)) {
  
  c_val <- c_fig[[n]]$data %>%
    group_by(node) %>%
    mutate (ave = mean (value)) %>%
    ungroup () %>%
    slice_max (ave, n = 6) %>%
    pull (node) %>%
    unique () %>%
    as.character()
  
  cat ("At", res$id[n], "across all three centrality measures, the two nodes with the greatest value was",     c_val[[1]], "and", c_val[[2]], "\n")

}


```


### Plot centrality stability

```{r message=FALSE, warning=FALSE, fig.height=15, fig.width=9}
# Plot centrality stability
s_fig <- map (res$centr_stb, plot, statistics = c("closeness", "strength", "betweenness"))

s_fig <- map (s_fig, ~.x + 
                ylab ("Ave Corr") + 
                  theme(text = element_text(size = 20), 
                        axis.text.x = element_text(angle = 90, hjust = 1)), 
              include = "all", print = FALSE, scale = "relative")


#tiff(width = 15, height = 15, units = "in", res = 100, file = "output/odi_stability.tiff")
cowplot::plot_grid(plotlist = s_fig, labels = res$id, vjust = 1, hjust = 0, ncol = 2, nrow = 3)
#dev.off()
```

```{r eval = FALSE, include = FALSE}
# expor
s_fig <- map (res$centr_stb, plot, statistics = c("closeness", "strength", "betweenness"))

s_fig <- map (s_fig, ~.x + 
                ylab ("Ave Corr") + 
                  theme(text = element_text(size = 20), 
                        axis.text.x = element_text(angle = 90, hjust = 1)), 
              include = "all", print = FALSE, scale = "relative")

pdf(width = 20, height = 15, file = "manuscript/fig4.pdf")
cowplot::plot_grid(plotlist = s_fig, 
                  labels = res$id, 
                    vjust = 1, hjust = 0, ncol = 2)
dev.off()

```

## Get CS coefficient

```{r, results = "asis", message=FALSE, warning=FALSE}
cs_coef <- res %>%
  select (id, cor_stb) %>%
  unnest () %>%
  ungroup() %>%
  mutate (measure = rep (c("betweenness", "closeness", "strength"), 6)) %>%
  mutate (CS = round (cor_stb, 2))
cs_coef %>%
  knitr::kable (caption = "Stability of centrality indices")

```

```{r eval = FALSE, include = FALSE}
my_path <- paste0("manuscript/table", 
                  "CScoef",
                  ".docx")


ft <- flextable(cs_coef) %>%
  set_caption(caption = "Table 2. CS Coefficient") %>%
  autofit()

my_doc <- read_docx()  %>% 
  body_add_flextable(ft) %>%
  body_end_section_landscape()

print (my_doc, target = my_path)
```

## Exploratory graphical analysis

```{reval = FALSE}
res <- res %>%
  mutate (ega = map (dat_norm, 
                     EGA, 
                     cor = "pearson",
                     model = "glasso",
                     model.args = list (tuning = 0.5,
                      lambda.min.ratio = 0.001,
                      corArgs =
                        list(method = "pearson",
                             use = "pairwise.complete.obs")),
                     algorithm = "walktrap",
                     plot.EGA = FALSE)) %>%
  mutate (cfa = pmap (list (ega.obj = ega, 
                            data = dat_norm),
                      CFA,
                      estimator = "WLSMV",
                      plot.CFA = FALSE)) 

# Bootstrap
ega_boot <- vector("list", length (res$id))
for (n in seq_along (res$id)) {
  
  ega_boot[[n]] <- bootEGA (res$dat_norm [[n]],
                             iter = 1000,
                             type = "resampling",
                             cor = "pearson",
                             model = "glasso",
                             algorithm = "walktrap",
                             plot.EGA = FALSE)
}
res$ega_boot <- ega_boot

```

## Stability

```{r, eval = FALSE}
ega_boot_stb <- vector("list", length (res$id))

for (n in seq_along (res$id)) {
  
  ega_boot_stb[[n]] <- dimStability (res$ega_boot[[n]], orig.wc = res$ega[[n]]$wc)
}

res$ega_boot_stb <- ega_boot_stb
```

### Summary table

```{r}

sum_df <- list()

for (n in seq_along (res$id)) {
  
  sum_df[[n]] <- res$ega_boot[[n]]$summary.table
}


sum_df <- bind_rows(sum_df) %>%
  mutate_if (is.numeric, round, 2)

sum_df$id <- res$id


sum_df
```

### Frequency 

```{r}
boot_freq <- res$ega_boot %>%
  map (pluck, "frequency") %>%
  map (as.data.frame)

names (boot_freq) <- res$id
boot_freq <-  bind_rows(boot_freq, .id = "id") 

boot_freq
```

## CFA 

```{r}
cfa_sum_list <- list()

for (n in seq_along(res$id)) {
  cfa_sum_list[[n]] <- lavaan::fitMeasures(res$cfa[[n]]$fit, fit.measures = "all")

}

cfa_sum <- cfa_sum_list %>%
  bind_rows() %>%
  mutate_if (is.numeric, round, 3) %>%
  mutate (id = res$id) %>%
  select (id, chisq.scaled, df, pvalue, cfi.scaled, rmsea.scaled )

cfa_sum
```

```{r eval = FALSE, include = FALSE}

# export
my_path <- paste0("manuscript/table3", 
                  "_cfa",
                  ".docx")


ft <- flextable(cfa_sum) %>%
  set_caption(caption = "Table 3. CFA") %>%
  autofit()

my_doc <- read_docx()  %>% 
  body_add_flextable(ft) 

print (my_doc, target = my_path)
```

## Compare networks

### Compare the networks for the RSI at 6th and 12th months

```{r, message=FALSE, warning=FALSE}
pair_res <- NCT (res$nw[[1]], 
             res$nw[[2]],
             it = 1000,
             paired = TRUE,
             test.edges = TRUE,
             progressbar = FALSE,
             test.centrality = TRUE,
             p.adjust.methods = "none",
             centrality = c("closeness", "strength", "betweenness"))
```


#### Edges which are different between networks

```{r}
pair_res$einv.pvals %>%
  filter (`p-value` < 0.05)
```

#### Centralities which are different between networks

```{r}
pair_res$diffcen.pval %>%
  as.data.frame() %>%
  filter_all (any_vars(. < 0.05))
```

### Compare the networks for the RSI at 6th month for those whose RTS value at 6mo was no vs yes

```{r, message=FALSE, warning=FALSE}
pair_res <- NCT (res$nw[[3]], 
             res$nw[[4]],
             it = 1000,
             paired = FALSE,
             test.edges = TRUE,
             progressbar = FALSE,
             test.centrality = TRUE,
             p.adjust.methods = "none",
             centrality = c("closeness", "strength", "betweenness"))
```


#### Edges which are different between networks

```{r}
pair_res$einv.pvals %>%
  filter (`p-value` < 0.05)
```

#### Centralities which are different between networks

```{r}
pair_res$diffcen.pval %>%
  as.data.frame() %>%
  filter_all (any_vars(. < 0.05))
```

### Compare the networks for the RSI at 12th month for those whose RTS value at 12mo was no vs yes

```{r, message=FALSE, warning=FALSE}
pair_res <- NCT (res$nw[[5]], 
             res$nw[[6]],
             it = 1000,
             paired = FALSE,
             test.edges = TRUE,
             progressbar = FALSE,
             test.centrality = TRUE,
             p.adjust.methods = "none",
             centrality = c("closeness", "strength", "betweenness"))

```


#### Edges which are different between networks

```{r}
pair_res$einv.pvals %>%
  filter (`p-value` < 0.05)
```

#### Centralities which are different between networks

```{r}
pair_res$diffcen.pval %>%
  as.data.frame() %>%
  filter_all (any_vars(. < 0.05))
```
